dump

### 2024-12-04 paper/dump.qmd
Complete Paper commit

model <- stan_glm(
  formula = total_building_permits ~ total_budget + average_household_income + population + ward_id,
  data = model_data,
  family = gaussian(link = "identity"),
  prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
  prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE)
)

@@

>>>>

model <- stan_glmer(
  formula = total_building_permits ~ total_budget + average_household_income + (1 | ward_id),
  data = model_data,
  family = gaussian(link = "identity"),
  prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
  prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE)
)

@@

# posterior predictive vs observed
posterior_vs_prior(model) +
  theme_minimal() +
  scale_color_brewer() +
  theme(legend.position = "bottom") +
  coord_flip()
